Turtlebot SLAM

### 2013-01-22 Article/Article.tex
Changed exploration. Evaluation is now explained correctly

Exploration does not only consist of finding frontiers. Based on the frontiers a target location for the robot needs to be selected. Navigating to frontier points directly is the simplest frontier-based exploration strategy. For this project, however, a more sophisticated implementation is chosen. Instead of sending the robot directly to a frontier point, a small search is performed to find suitable destinations. Generally, a small region around the frontier cell is searched. The goal is to find a cell with as much free space around it as possible. For this purposes an evaluation function has been implemented. It incorporates three features that are used to send a goal to the robot's navigation stack. The three features are :
\begin{enumerate}
\item{Number of obstacles in the area}
\item{Distance to the previous goal}
\item{Distance between frontier and robot location}
\end{enumerate}
The first two features have equal weights, whereas the third gets a weight of 5. This configuration turned out to create the best results (see Subsection \ref{sec:navEval}) Their weighted sum is used to find the final goal to be sent to the navigation stack. This evaluation function enables the algorithm to select a reachable destination for the robot in almost every case. Additionally the information gain is still next to optimal since the selected goal is preferred to be close to frontier points. At last the third feature makes sure that the robots path is smooth. Selecting a goal near the previous one makes the robot avoid to many loops in the emerging graph.
\subsection{Graph SLAM}
\label{sec:implSLAM}
Two different approaches of graph-based SLAM are implemented for this project. They differ in complexity and thereby applicability to the problem. Both algorithms create an occupancy grid map. 
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/graph.png}
	\caption{An example of a simple graph (based on \citep{Grisetti}).}
	\label{fig:turtlebotexample_graph}
\end{figure}
First, an algorithm as suggested in \citep{Grisetti} is implemented. Here the graph consists of nodes representing poses along the robot trajectory. Odometry and sensor measurements are incorporated into the constraints contained in the edges. Similar to the Graph SLAM procedure explained in Section \ref{subsec:sotaSlam}, an edge connects two adjacent poses of the robot. This implementation optimizes the pose graph according to the constraints. This ``optimized" trajectory then determines the positions of obstacles on the map by refining the laser scan data according to the poses they were obtained at. Each edge thus is labeled with the spatial difference between two poses \(x_i\) and \(x_j\). Let this error be denoted by \(e_{ij}(x_i, x_j)\). This information is obtained from a combination of odometry data and laser range sensor data. In fact, the odometry is corrected using a laser scan matcher (see Subsection \ref{sec:scan}).

>>>>

Exploration does not only consist of finding frontiers. Based on the frontiers a target location for the robot needs to be selected. Navigating to the closest frontier points is the simplest frontier-based exploration strategy. For this project, however, a more sophisticated implementation is chosen. Instead of sending the robot to the closest frontier point, a small search is performed to find suitable destinations. Generally, a small region around each frontier cell is searched. The goal is to give each frontier point a rating on how well it is suited as a destination. For this purposes an evaluation function has been implemented. It incorporates three features that are used to evaluate goals to be sent to the navigation stack. They are :
\begin{enumerate}
\item{Number of obstacles in the area}
\item{Distance to the previous goal}
\item{Distance between frontier and robot location}
\end{enumerate}
The first two features have a weight one, whereas the third is assigned a weight of five. This configuration turned out to create the best results (see Subsection \ref{sec:navEval}) The weighted sum of the features is used to find the goal to be sent to the navigation stack. This evaluation function enables the algorithm to select a reachable destination for the robot in almost every case. The frontier cells are sent to the move\_base in the order of the rating. When the navigation stack fails to steer the robot to a designated goal within a time constraint, the next best goal replaces the previous. The information gain is still next to optimal since the selected goal is preferred to be close to frontier points. At last the second feature makes sure that the robots path is smooth. Selecting a goal near the previous one makes the robot avoid too many loops in the emerging graph.
\subsection{Graph SLAM}
\label{sec:implSLAM}
Two different approaches of graph-based SLAM are implemented for this project. They differ in complexity and thereby applicability to the problem. Both algorithms create an occupancy grid map. 
\begin{figure}[h]
	\centering
		\includegraphics[width=0.50\textwidth]{figures/graph.png}
	\caption{An example of a simple graph (based on \citep{Grisetti}).}
	\label{fig:turtlebotexample_graph}
\end{figure}
First, an algorithm as suggested in \citep{Grisetti} is implemented. Here the graph consists of nodes representing poses along the robot trajectory. Odometry and sensor measurements are incorporated into the constraints contained in the edges. Similar to the Graph SLAM procedure explained in Section \ref{subsec:sotaSlam}, an edge connects two adjacent poses of the robot. This implementation optimizes the pose graph according to the constraints. This ``optimized" trajectory then determines the positions of obstacles on the map by refining the laser scan data according to the poses they were obtained at. Each edge thus is labeled with the spatial difference between two poses \(x_i\) and \(x_j\). Let this error be denoted by \(e_{ij}(x_i, x_j)\). This information is obtained from a combination of odometry data and laser range sensor data. In fact, the odometry is corrected using a laser scan matcher (see Subsection \ref{sec:scan}).
